First off, I would like to thank my advisor, Dr. Alexander Khanov. Without his guidance and patience, my experience through 
graduate school could have been very different. Dr. Khanov accepted me as an REU student 6 years ago and introduced me to particle physics.
The memorable time I had with him, and the team influenced my decision on choosing Oklahoma State University for graduate
school which has completely changed my life. He has been a pivotal role, and I cannot thank him enough for being that.
Dr. Flera Rizatdinova, thank you for your caring leadership. You're a vital piece that is required for the unity of our team.
\par
I would also like to thank The High Energy Physics team at Oklahoma State University. You all have been my physics family 
and have truly been a large part of this special experience. To my fellow graduate friends and colleagues. You have all helped 
make OSU feel like home and I hope you find the warmth in others as I found in all of you. 
Sincere thanks to Dr. Alexander Khanov, Dr. K. S. Babu, Dr. Mario Borunda, and Dr. Cong Pu for accepting to be on my dissertation advisory committee.
\par
To my friends overseas at CERN, thank you for making unforgettable memories with me and showing me how truly American I really am. Huge 
thanks to Luke, Chetna and Fabienne who acted with great urgency when I had a cooking accident making gnocchi, you all get two thumbs up. I would 
like to thank my colleagues in the Flavor Tagging team who helped reinforce my confidence and supplied guidance when sought. 
\par
I would like to thank the anomaly detection analysis team, Sergei Chekanov, Rui Zhang, and Wasikul Islam. Our synergy brought 
our analysis into fruition and helped pave the way for similar techniques. May you all remain innovative and efficient. 
\par
Not many times in one's life do they get to experience a pandemic during their graduate degree. I would like to give credit to all those 
within OSU and the physics department for their patience and dedication to education, even through such chaos. We all certainly lived in interesting times. 
\par
Of course, my beloved family who have always been there with necessary support and have always had my back. I Love you all.
Robyn Edwards, without this nexus of choices and people, we would never have met. I can never be thankful enough to the aligned stars 
that brought you into my life.
\par
Lastly, I want to dedicate this thesis to my cousin and best friend who has passed before his time. Drew, I know you would be proud. 
This one is for you. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% NOTICE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% If you Acknowledgments span MORE than one page, the graduate college
% requires that you have this footer present on every page. In order to put it
% there, you will put this footer command in some of the text on page 2 (or 3,
% etc.) in order to ensure a copy of the footer appears on each page:

\blfootnote{Acknowledgments reflect the views of the author and are not endorsed
 by committee members or Oklahoma State University.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
